%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\documentclass{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}  % Added for \href commands
\usepackage{ifthen}

\newcommand{\position}{Research PM}
\newcommand{\company}{Anthropic}

% Define a macro to get the correct article
\newcommand{\getarticle}[1]{%
  \ifthenelse{
    \equal{\string\position}{A} \OR
    \equal{\string\position}{E} \OR
    \equal{\string\position}{I} \OR
    \equal{\string\position}{O} \OR
    \equal{\string\position}{U}
  } 
  {an}{a}%
}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eric}{Crisp}{\urlstyle{same}{ecrisp@upenn.edu} | +1 (302) 528 - 2477 | \urlstyle{same}\href{https://linkedin.com/in/ecrisp}{linkedin.com/in/ecrisp}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{\company}
\vspace{0.5cm}
% \companyaddress{}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear \company{}'s Hiring Team,}

\lettercontent{I am writing to express my strong interest in the \position{} role at \company{}. My career has been driven by a commitment to solving impactful engineering challenges — first in aerospace, where I helped make access to space more reliable and affordable, and now in AI/ML research where there is immense potential to create ethical, transformative solutions. This passion led me to make a deliberate career transition, leaving aerospace to pursue a Master of Science in Data Science with AI/ML concentration at the University of Pennsylvania.}

\lettercontent{Working at the cutting edge of both aerospace and AI/ML has revealed fundamental similarities that make my transition both natural and valuable. Both fields demand the ability to synthesize complex, interdisciplinary knowledge—from advanced mathematics and systems-level thinking to software engineering all while maintaining the ability to see the forest through the trees - a skill necessary to drive ambitious, complex projects to completion under uncertainty.}

\lettercontent{With years of exposure to scientific programming, linear algebra, and applied mathematics, I had an ideal launching point for a career in machine learning. My graduate studies at Penn exposed me to essential toolkits for modern AI/ML: database architectures, distributed computing, statistical modeling, and machine learning frameworks. This dual perspective allows me to approach problems with both an engineer's systematic rigor and a data scientist's analytical creativity, enabling me to build solutions that are not only theoretically sound but also practically robust and scalable.}

\lettercontent{My background brings distinctive value that directly translates to this role. At Firefly Aerospace, I collaborated with two other engineers to design, build, and test an engine system that would go on to successfully land on the Moon in 2025. This experience taught me to navigate the complete product lifecycle—from stakeholder communication and technical trade-offs to delivering results under extreme pressure and timeline constraints.} 

\lettercontent{At Blue Origin, I took on an even greater challenge: transforming an abstract business concept into a production-ready software solution with minimal guidance and tight deadlines. In just four months, I developed the Real-Time Model (RTM), which not only exceeded initial objectives but remains a cornerstone product today. As the project's success became evident, my responsibilities expanded from individual contributor to technical leader, where I managed an engineering team, guided product strategy, and developed the leadership skills essential for driving complex initiatives to completion.}

\lettercontent{What truly drives me is the recognition that AI/ML products will profoundly impact countless lives across socioeconomic communities. This responsibility demands that every solution we build be unequivocally ethical, safe, and robust. This conviction motivated my career transition and fuels my commitment to contributing meaningfully to responsible AI/ML development and solutions. I am excited about the opportunity to bring this passion, along with my unique technical background and proven track record of delivering high-impact results, to the \position{} role at \company{}.}


\lettercontent{Thank you for considering my application. I look forward to discussing how my experience and dedication can contribute to \company{}'s mission.}

% \vspace{0.1cm}
\closing{Sincerely}{Eric Crisp}
\end{document}