%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\documentclass{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}  % Added for \href commands
\usepackage{ifthen}

\newcommand{\position}{Research PM}
\newcommand{\company}{Anthropic}

% Define a macro to get the correct article
\newcommand{\getarticle}[1]{%
  \ifthenelse{
    \equal{\string\position}{A} \OR
    \equal{\string\position}{E} \OR
    \equal{\string\position}{I} \OR
    \equal{\string\position}{O} \OR
    \equal{\string\position}{U}
  } 
  {an}{a}%
}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eric}{Crisp}{\urlstyle{same}{ecrisp@upenn.edu} | +1 (302) 528 - 2477 | \urlstyle{same}\href{https://linkedin.com/in/ecrisp}{linkedin.com/in/ecrisp}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{\company}
\vspace{0.5cm}
% \companyaddress{}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear \company{}'s Hiring Team,}

\lettercontent{

When I started my career and selected aerospace engineering, it wasn't because I had a passion for traveling to Mars or landing on the Moon. It was because of a paper I read from Caltech on transmitting solar power wirelessly (SSPP). In part, the authors argued that commercial access to space for relocating resource, or pollution, intensive industries would benefit everyone on earth (e.g., moving solar farms to orbit). This is fundamental to my underlying motivation through my career: engineering can be used to scale my impact via ethical solutions to large-scale problems that benefit members of society without distinction.

}

\lettercontent{
 I resaerched clean combustion for five years to help progress the emissions problem; I joined Blue Origin to help build reusable, clean rockets designed to relocate polluting industries to space; Now, my focus has shifted to AI safety and ethical implementations of AI technologies to help level an increasing disparate society. Not only is AI developing at an alarming rate, but the related products being released are impacting societies, industries, and governments across many socioeconomic boundaries. People are being exposed to these technologies, sometimes without even knowing it, putting not only regulations and laws in the hot seat but also placing an enormous ethical responsibility on industry leaders.

}

\lettercontent{

That is why I am applying here. From the very beginning, Anthropic has fundamentally realized their impact and responsibility to the public. This organization has shown commitment to transparency, rigorous safety practices, and cutting edge research time and time again through almost 5 years of publicly available resources, open source development, and even structuring the company as a PBC that makes me want to continue my career at Anthropic.

}

\lettercontent{

With years of engineering experience, graduate work in data science and machine learning, and a genuine passion for the mission - I am interested in pursuing a role where my effort will be the most impactful and the most useful. Bringing a balance of eagerness, aptitude, and a unique technical background, I hope to find a place to help Anthropic bring ethically sound, high value, and high impact AI solutions to the public including less fortunate and underrepresented regions and communities.

}

% \vspace{0.1cm}
\closing{Sincerely}{Eric Crisp}
\end{document}

