%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\documentclass{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}  % Added for \href commands
\usepackage{ifthen}

\newcommand{\position}{Research PM}
\newcommand{\company}{Anthropic}

% Define a macro to get the correct article
\newcommand{\getarticle}[1]{%
  \ifthenelse{
    \equal{\string\position}{A} \OR
    \equal{\string\position}{E} \OR
    \equal{\string\position}{I} \OR
    \equal{\string\position}{O} \OR
    \equal{\string\position}{U}
  } 
  {an}{a}%
}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eric}{Crisp}{\urlstyle{same}{ecrisp@upenn.edu} | +1 (302) 528 - 2477 | \urlstyle{same}\href{https://linkedin.com/in/ecrisp}{linkedin.com/in/ecrisp}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{\company}
\vspace{0.5cm}
% \companyaddress{}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear \company{}'s Hiring Team,}

\lettercontent{

When I started my engineering career and selected aerospace engineering, it wasn't because I had a passion for traveling to Mars, or landing on the Moon. It was because of a paper I read on Caltech's wireless solar power (SSPP). In part, it argued that commercial access to space as an engineering solution to relocate resource, or pollution, intensive industries, such as solar farms, would be a benefit for everyone on earth - high impact. I saw it as more than a chance to lower greenhouse emissions. I saw it as non-harmful path to a space-race like industry prompting a surge in technology development. After all, we have the first space-race to thank for countless life saving inventions.}

\lettercontent{
However, over the past few years, I took inventory of the engineering landscape and decided the rate of impact I was contributing to in the space industry was marginalized by the scale and rate of impact occurring in tech, specifically artificial intelligence. Not only are things happening quickly, but things are happening across socioeconomic boundaries. People are being exposed to these technologies, sometimes without even knowing it now, putting not only regulations and laws in the hot seat, but also an enormous ethical responsibility on industry leaders such as Anthropic.}

\lettercontent{
Anthropic, however, is one company that has, from the beginning, fundamentally realized their impact and responsibility in the sector and puts safety, regulation, and ethical development above all else. It's shown time and time again through almost 5 years of publicly available research, open source development, and a people-first culture that makes me want to continue my career at Anthropic.}

\lettercontent{
With years of engineering experience, graduate work in data science and machine learning, and a genuine passion for the mission - I am interested in pursuing a role where my effort will be the most impactful, and the most useful. Bringing a balance of eagerness, aptitude, and a unique background, I hope to find a place to help Anthropic bring ethically sound, high value, and high impact AI products to underrepresented regions and communities.}

% \vspace{0.1cm}
\closing{Sincerely}{Eric Crisp}
\end{document}