%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cover Letter Template
% LaTeX Template
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
\documentclass{cover}
\usepackage{fancyhdr}
\usepackage{hyperref}  % Added for \href commands
\usepackage{ifthen}

\newcommand{\position}{Research PM}
\newcommand{\company}{Anthropic}

% Define a macro to get the correct article
\newcommand{\getarticle}[1]{%
  \ifthenelse{
    \equal{\string\position}{A} \OR
    \equal{\string\position}{E} \OR
    \equal{\string\position}{I} \OR
    \equal{\string\position}{O} \OR
    \equal{\string\position}{U}
  } 
  {an}{a}%
}

\pagestyle{fancy}
\fancyhf{}
 
\rfoot{Page \thepage \hspace{1pt}}
\thispagestyle{empty}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Eric}{Crisp}{\urlstyle{same}{ecrisp@upenn.edu} | +1 (302) 528 - 2477 | \urlstyle{same}\href{https://linkedin.com/in/ecrisp}{linkedin.com/in/ecrisp}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     MAIN COVER LETTER CONTENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hfill

\begin{minipage}[t]{0.5\textwidth} 
\companyname{\company}
\vspace{0.5cm}
% \companyaddress{}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth} 
\currentdate{\today}
\end{minipage}

\lettercontent{Dear \company{}'s Hiring Team,}

\lettercontent{

When I started my career and selected aerospace engineering, it wasn't because I had a passion for traveling to Mars or landing on the Moon. It was because of a paper I read from Caltech on transmitting solar power wirelessly (SSPP). In part, the authors argued that commercial access to space for relocating resource, or pollution, intensive industries would benefit everyone on earth (e.g., moving solar farms to orbit). This is fundamental to my underlying motivation through my career: engineering can be used to scale my impact via ethical solutions to large-scale problems that benefit members of society without distinction.

}

\lettercontent{
 My career started with years of researching clean combustion hoping to progress the emissions problem. I then joined Blue Origin to help build clean, reusable rockets designed to relocate polluting industries to space. Now, my focus has shifted towards ethical, safe development and implementations of AI technologies that hopefully empower individuals across socioeconomic boundaries to achieve what may not have been otherwise possible while simultaneously helping address critical problems like cancer research, clean energy, and world hunger. 
 
}

\lettercontent{ 
  
With the field's breakneck development cycle, these transformative technologies are being deployed faster than we can fully assess their societal impact. As these systems become invisibly integrated into daily life, we face a regulatory lag that puts enormous pressure on industry leaders to self-regulate and consider the broader implications of the innovations.

}

\lettercontent{

That is why I am applying here. From the very beginning, Anthropic has fundamentally realized their impact and responsibility to the public. This organization has shown commitment to transparency, rigorous safety practices, and cutting edge research time and time again through almost six years of publicly available resources, open source development, and even structuring as a PBC.

}

\lettercontent{

I bring a distinctive combination of industry experience, graduate work in machine learning and artifical intelligence, and a deep, personal alignment with Anthropic's mission. My success navigating complex challenges to completion across multiple technical domains from clean combustion to reusable rockets has prepared me to contribute to the deveopment of responsible AI technologies with real-world impact.

}

% \vspace{0.1cm}
\closing{Sincerely}{Eric Crisp}
\end{document}

